Timeliness of security updates for Android

### 2014-08-06 securityupdates.tex
Add subsection heading for android update process
Include statistics on upgrade and downgrade events

\subsection{Running a version of Android known to be vulnerable makes a device vulnerable}
While we have not tried to exploit these vulnerabilities on the devices in order to test whether the devices are actually vulnerable, we are confident that most devices will be if they are running a vesion known to be vulnerable.

@@

\subsection{Update frequency}
%TODO find out what the frequency of updates is
\begin{figure}
 \includegraphics[width=0.5\textwidth]{figures/from_to_updates.pdf}
 \caption{Updates between different Android versions in the DA data}
 \label{fig:from_to_updates}
\end{figure}
\begin{figure}
 \includegraphics[width=0.5\textwidth]{figures/w_security_updates.pdf}
 \caption{Number of updates each week which fixed or may have fixed security vulnerabilities}
 \label{fig:weekly_security_updates}
\end{figure}
Figure~\ref{fig:from_to_updates} shows how devices upgrade between different versions of Android.
Device Analyzer (DA) observes upgrade events and the figure shows which versions a device is upgrading from and to.
Mostly the dark cells are above the diagonal and are upgrades.
While many upgrades are from one version to the next version there are also a fair number which skip a few versions.
Surprisingly there are also a small number of downgrade events when older versions of Android are installed on to devices.
The number of devices getting security updates each week, is shown in Figure~\ref{fig:weekly_security_updates}, blue shows updates which changed the Android version number from a version with known vulnerabilities to one which had fewer known vulnerabilities.
Red indicates updates which changed the build number but not the version number and so might contain a backported fix for a vulnerability.
%TODO summary stats, what does this mean

>>>>

\subsection{Running a version of Android known to be vulnerable makes a device vulnerable}
While we have not tried to exploit these vulnerabilities on the devices in order to test whether the devices are actually vulnerable, we are confident that most devices will be if they are running a vesion known to be vulnerable. %TODO WHY?

\subsection{Android update process}
TODO

@@

\subsection{Update frequency}
%TODO find out what the frequency of updates is
\begin{figure}
 \includegraphics[width=0.5\textwidth]{figures/from_to_updates.pdf}
 \caption{Updates between different Android versions in the DA data}
 \label{fig:from_to_updates}
\end{figure}
\begin{figure}
 \includegraphics[width=0.5\textwidth]{figures/w_security_updates.pdf}
 \caption{Number of updates each week which fixed or may have fixed security vulnerabilities}
 \label{fig:weekly_security_updates}
\end{figure}
Figure~\ref{fig:from_to_updates} shows how devices upgrade between different versions of Android.
Device Analyzer (DA) observes upgrade events and the figure shows which versions a device is upgrading from and to.
Mostly the dark cells are above the diagonal and are upgrades (\daNumUpdatesUpgrades).
While many upgrades are from one version to the next version there are also a fair number which skip a few versions.
Surprisingly there are also a small number of downgrade events (\daNumUpdatesDowngrades, \daPercUpdatesDowngrades) when older versions of Android are installed on to devices.

The number of devices getting security updates each week, is shown in Figure~\ref{fig:weekly_security_updates}, blue shows updates which changed the Android version number from a version with known vulnerabilities to one which had fewer known vulnerabilities.
Red indicates updates which changed the build number but not the version number and so might contain a backported fix for a vulnerability.
%TODO summary stats, what does this mean
